\texttt{SuperScreen}

### 2021-07-16 main.tex
Add citations

\SuperScreen is an open-source Python package developed to simulate the magnetic response of structures composed of one or more layers containing superconducting thin films. \SuperScreen solves the coupled Maxwell's and London's equations in and around superconducting films with spatially-varying penetration depth in the presence of applied magnetic fields and trapped flux using a matrix inversion method introduced by Brandt [ref.] and initially implemented by Kirtley [ref, ref] to model the magnetic response of scanning superconducting quantum interference device (SQUID) sensors.

@@

A convenient method for solving this problem was introduced in [Brandt-PRB-2005], and used in [Kirtley-RSI-2016] and [Kirtley-SST-2016] to model the magnetic response of scanning Superconducting Quantum Interference Device (SQUID) susceptometers.

@@

where $\Lambda(x, y)=\lambda^2(x, y)/d$ is the effective penetration depth
of the superconducting film (equal to half the Pearl length [Pearl-APL-1964]).

It is important to note that the assumption $\vec{j}(x, y, z)\approx\vec{j}_{z_0}(x, y)$ is valid for only films that are thinner than their London penetration depth ($d<\lambda$, such that $\Lambda=\lambda^2/d>\lambda$). However the model has been applied with some success in structures with $\lambda\lesssim d$ [Kirtley-RSI-2016] [Kirtley-SST-2016]. Aside from this limitation, the method described below can in principle to used to model films with any effective penetration depth $0\leq\Lambda<\infty$.

@@

The stream function $g$ can be thought of as the local magnetization of the film, or the area density of magnetic dipole sources (see [Brandt] for more interesting properties of the stream function). We can re-write Eq.~\ref{eq:london} for a 2D film in terms of $g$:

@@

The kernel matrix $\mathbf{Q}$ and weight matrix $\mathbf{w}$ together play the role of the
kernel function $Q_z(\vec{r},\vec{r}')$ for all points lying in the plane of the film. They are both $n\times n$ matrices determined solely by the geometry of the mesh.
$\mathbf{h}_z$, $\mathbf{h}_{z,\,\mathrm{applied}}$, and $\mathbf{g}$ are all $n\times 1$ vectors, with each row representing the value of the quantity at the
corresponding vertex in the mesh. There are several different methods for constructing the weight matrix $\mathbf{w}$, which are discussed in Section[] below. The kernel
matrix $\mathbf{Q}$ is defined in terms of a matrix with
$(\mathbf{q})_{ij} = \left(4\pi|\vec{r}_i-\vec{r}_j|^3\right)^{-1}$
(which is $\lim_{\Delta z\to 0}Q_z(\vec{r},\vec{r}')$ cf. Eq.~\ref{eq:kernels}),
and a vector $\mathbf{C}$:

\begin{equation}
    \label{eq:kernel_matrix}
    Q_{ij} = (\delta_{ij}-1)q_{ij}
    + \delta_{ij}\frac{1}{w_{ij}}\left(C_i + \sum_{l\neq i}q_{il}w_{il}\right),
\end{equation}
where $\delta_{ij}$ is the Kronecker delta function. The diagonal terms involving $\mathbf{C}$ are meant to work around the fact that $q_{ii}$ diverge (see [Brandt-PRB-2005] for more details), and the vector is defined as

@@

\begin{equation}
    \label{eq:Heff_sub_num}
     \mathbf{h}_{z,\,\mathrm{applied}} - \sum_{\mathrm{holes}\, k}\mathbf{h}_{z,\,\mathrm{eff},\,k} = -(\mathbf{Q}\cdot\mathbf{w}-\mathbf{\Lambda}\cdot\mathbf{\nabla}^2)\mathbf{g},
\end{equation}
where we exclude points in the mesh lying outside of the superconducting film, but keep points
inside holes in the film. $\mathbf{\Lambda}$ is either a scalar or a vector defining the effective penetration depth at every included vertex in the mesh, and $\mathbf{\nabla}^2$
is the Laplace operator (see Section[]), an $n\times n$ matrix defined such that $\mathbf{\nabla}^2\mathbf{f}$ computes the Laplacian $\nabla^2f(x,y)$ of a function $f(x,y)$ defined on the mesh.

@@

>>>>

\SuperScreen is an open-source Python package developed to simulate the magnetic response of structures composed of one or more layers containing superconducting thin films. \SuperScreen solves the coupled Maxwell's and London's equations in and around superconducting films with spatially-varying penetration depth in the presence of applied magnetic fields and trapped flux using a matrix inversion method introduced by Brandt~\cite{brandt_thin_2005} and initially implemented by Kirtley, \emph{et al.}~\cite{kirtley_scanning_2016, kirtley_response_2016} to model the magnetic response of scanning superconducting quantum interference device (SQUID) sensors.

@@

A convenient method for solving this problem was introduced in~\cite{brandt_thin_2005}, and used to model the magnetic response of scanning Superconducting Quantum Interference Device (SQUID) susceptometers~\cite{kirtley_scanning_2016, kirtley_response_2016}.

@@

where $\Lambda(x, y)=\lambda^2(x, y)/d$ is the effective penetration depth
of the superconducting film (equal to half the Pearl length~\cite{pearl_current_1964}).

It is important to note that the assumption $\vec{j}(x, y, z)\approx\vec{j}_{z_0}(x, y)$ is valid for only films that are thinner than their London penetration depth ($d<\lambda$, such that $\Lambda=\lambda^2/d>\lambda$). However the model has been applied with some success in structures with $\lambda\lesssim d$~\cite{kirtley_scanning_2016,kirtley_response_2016}. Aside from this limitation, the method described below can in principle to used to model films with any effective penetration depth $0\leq\Lambda<\infty$.

@@

The stream function $g$ can be thought of as the local magnetization of the film, or the area density of magnetic dipole sources (see \cite{brandt_thin_2005} for more interesting properties of the stream function). We can re-write Eq.~\ref{eq:london} for a 2D film in terms of $g$:

@@

The kernel matrix $\mathbf{Q}$ and weight matrix $\mathbf{w}$ together play the role of the
kernel function $Q_z(\vec{r},\vec{r}')$ for all points lying in the plane of the film. They are both $n\times n$ matrices determined solely by the geometry of the mesh.
$\mathbf{h}_z$, $\mathbf{h}_{z,\,\mathrm{applied}}$, and $\mathbf{g}$ are all $n\times 1$ vectors, with each row representing the value of the quantity at the
corresponding vertex in the mesh. There are several different methods for constructing the weight matrix $\mathbf{w}$, which are discussed in Section~\ref{section:implementation:laplace} below. The kernel
matrix $\mathbf{Q}$ is defined in terms of a matrix with
$(\mathbf{q})_{ij} = \left(4\pi|\vec{r}_i-\vec{r}_j|^3\right)^{-1}$
(which is $\lim_{\Delta z\to 0}Q_z(\vec{r},\vec{r}')$ cf. Eq.~\ref{eq:kernels}),
and a vector $\mathbf{C}$:

\begin{equation}
    \label{eq:kernel_matrix}
    Q_{ij} = (\delta_{ij}-1)q_{ij}
    + \delta_{ij}\frac{1}{w_{ij}}\left(C_i + \sum_{l\neq i}q_{il}w_{il}\right),
\end{equation}
where $\delta_{ij}$ is the Kronecker delta function. The diagonal terms involving $\mathbf{C}$ are meant to work around the fact that $q_{ii}$ diverge (see \cite{brandt_thin_2005} for more details), and the vector is defined as

@@

\begin{equation}
    \label{eq:Heff_sub_num}
     \mathbf{h}_{z,\,\mathrm{applied}} - \sum_{\mathrm{holes}\, k}\mathbf{h}_{z,\,\mathrm{eff},\,k} = -(\mathbf{Q}\cdot\mathbf{w}-\mathbf{\Lambda}\cdot\mathbf{\nabla}^2)\mathbf{g},
\end{equation}
where we exclude points in the mesh lying outside of the superconducting film, but keep points
inside holes in the film. $\mathbf{\Lambda}$ is either a scalar or a vector defining the effective penetration depth at every included vertex in the mesh, and $\mathbf{\nabla}^2$
is the Laplace operator (see Section~\ref{section:implementation:laplace}), an $n\times n$ matrix defined such that $\mathbf{\nabla}^2\mathbf{f}$ computes the Laplacian $\nabla^2f(x,y)$ of a function $f(x,y)$ defined on the mesh.

@@

\bibliographystyle{plain}
\bibliography{references}
